% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifxetex
  % Load bidi as late as possible as it modifies e.g. graphicx
  \usepackage{bidi}
\fi
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \TeXXeTstate=1
  \newcommand{\RL}[1]{\beginR #1\endR}
  \newcommand{\LR}[1]{\beginL #1\endL}
  \newenvironment{RTL}{\beginR}{\endR}
  \newenvironment{LTR}{\beginL}{\endL}
\fi

\date{}

\begin{document}
    \title{\begin{flushleft}SHIVANAND VELMURUGAN\end{flushleft}}
    \begin{flushright}\textsc{PRODUCT LEADER}\end{flushright}

\LR{Vancouver, British Columbia • +1 (778) 881-2468 •
\href{mailto:shiv@shiv.me}{{shiv@shiv.me}} •
\href{https://www.linkedin.com/in/vshivanand/}{{LinkedIn}}}

\LR{\textbf{Effective Product Leader} with experience in design and
development of software products. An inquisitive problem-solver that
drives decisions based on a data-driven first-principles approach.
Excellent communication, collaboration, and organizational skills. Adept
in building and working with high-performing engineering teams.
Demonstrated success in tackling hard engineering problems and
delivering products and solutions that have an impact on the
organization.}

\LR{}

\textbf{\LR{Key Strengths}}

\LR{\emph{Strategic Thinking} \textbar{} \emph{Data Collection \&
Organization} \textbar{} \emph{People Connector} \textbar{} \emph{Leader
\& Mentor}}

\LR{}

\LR{\textbf{PROFESSIONAL EXPERIENCE}}

\LR{\textbf{GE DIGITAL} Burnaby, British Columbia \textbf{2017-Present}}

\textbf{\LR{Staff Technical Product Manager}}

\emph{\LR{Reporting to the Director of Product, accountable for two key
GE Digital products: Predix Studio and Predix AppEngine. Target markets
include GE business verticals of power, mining, aviation, and
healthcare. Total addressable revenue potential: 100M+.}}

\textbf{\LR{Key Accomplishments:}}

\begin{itemize}
\item
  \LR{Successfully drove impactful architectural changes to enable
  access to verticals including healthcare and aviation.}
\item
  \LR{Instituted a data-driven approach to product roadmap definition
  and planning, resulting in a shift to a continuous improvement model
  of developing products.}
\item
  \LR{Initiated and drove the adoption of GE security policies reducing
  the number of security issues from 1000+ to zero.}
\item
  \LR{Led engineering teams to focus on product quality improvement by
  creating team alignment initiatives. Reduced bugs from 3000+ to less
  than 200 in 1 year.}
\item
  \LR{Reduced operational cost by streamlining product infrastructure,
  testing practices and instituting CI/CD. Created clarity on customer
  offering and cost to serve, and reduced bug incidence during
  regression by \textasciitilde300\% YoY.}
\end{itemize}

\LR{}


\LR{\textbf{ERICSSON INC. (HCL Axon Technologies, Redback Networks)}
Burnaby, British Columbia \textbf{2007-2017}}

\emph{\LR{Progressive career and reporting structures, beginning with
Redback Networks as part of the Ericsson Inc. Organization. Begaan as
Senior Software Engineer, moving into Team Lead and Product Owner.}}

\LR{\textbf{Product Owner} (2014-2017)}

\emph{\LR{Reporting to a Senior Manager, defined vision, strategy and
roadmap for next-gen declarative application development on Ericsson
IPOS product line.}}

\textbf{\LR{Key Accomplishments:}}

\begin{itemize}
\item
  \LR{Secured executive buy-in and investment in multi-year
  infrastructure projects. Effectively prioritized and shaped
  requirements from multiple stakeholders, including developers, system
  managers and product sponsors within Ericsson.}
\item
  \LR{Built and mentored multiple agile product development teams across
  North America and East Asia. multiple sites and time-zones. Leveraged
  agile methodologies to successfully develop high performing teams to
  deliver key projects on time and within budget.}
\item
  \LR{Migrated six applications within three months resulting in reduced
  code base by up to 80\%; increased developer productivity by two to
  three times; and, improved time to market from months to days.}
\end{itemize}

\textbf{\LR{Engineer/Architect}}

\emph{\LR{Reporting to a Senior Manager, led and managed diverse product
improvement initiatives in various domains including core
infrastructure, configuration management, and license management for a
carrier class router operating system.}}

\textbf{\LR{Key Accomplishments:}}

\begin{itemize}
\item
  \LR{Successfully designed, developed and operationalized a set of
  components for managing schema-based data using a high-performance
  database in carrier-class router operating system.}
\item
  \LR{Designed common models for IPOS and evangelized Ericsson Common
  Information Model and its adoption across IPOS features including
  setting standards, establishing a technical council of developers
  proficient in modeling, training and mentoring them to work with IPOS
  feature teams.}
\item
  \LR{Created a meta-data aware, non-transactional cache. Created a
  high-density, low-latency, transactional datastore with record-level
  locking.}
\item
  \LR{Shortened development cycle from hours to seconds by redesigning
  build infrastructure for IPOS platform and components.}
\item
  \LR{Wrote a custom DSL to provide Object Relationship Mapping between
  two proprietary data definition languages.}
\item
  \LR{Implemented Python and JavaScript apps to demonstrate MDI's
  abilities as an ecosystem for rapid app development using SWIG and
  FFI.}
\end{itemize}

\LR{\textbf{PREVIOUS PROFESSIONAL EXPERIENCE}}

\LR{
    \textbf{Novell,} Bangalore, India, Senior Software Engineer\\
    \textbf{HCL Technologies (Cisco Partner),} Chennai, India, Lead Engineer\\
    \textbf{Intec Solutions}, Chennai, India, Software Engineer
}

\LR{\textbf{EDUCATION \& PROFESSIONAL DEVELOPMENT}}

\LR{
    \textbf{Bachelor of Technology, Electrical \& Electronics Engineering,} Pondicherry Engineering College, India\\
    \textbf{Disruptive Strategy Certificate}, Clayton Christensen, Harvard School of Business
}

\LR{\textbf{SKILLS}}

\LR{Proven expertise in product management, architecture and design of
high-performance and high-scale industrial software, databases and IP
operating systems. Expert in C and C++, with an emphasis on development
in embedded systems.}

\LR{\textbf{Product Management:} JTBD Theory, Product strategy,
Disruptive Innovation Theory, Lean Startup\\
\textbf{Languages} : C, C++, Java, Javascript, Python, BASH, Perl, Ruby,
Go, Rust, Nimrod, Terra\\
\textbf{Build Tools} : CMake, Make, Ninja\\
\textbf{Source Control} : Git, CVS, SVN, Mercurial, Clearcase\\
\textbf{Miscellaneous} : XML, XSLT, SOAP, XQUERY, SWIG, ANTLR,
Flex/Bison, JSON, REST\\
\textbf{Networking}: NETCONF, RESTCONF, SNMP, several L2 and L3
protocols\\
\textbf{Cloud} : UAA, Cloudfoundry, several AWS, GCP and Azure products}

\end{document}
